\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}
\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------RESUME STARTS HERE----------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ram Goenka} \\ \vspace{1pt}
    \small 217-974-1713 $|$ \href{mailto:rgoenka2@illinois.edu}{\underline{rgoenka2@illinois.edu}} $|$ 
    \href{https://www.linkedin.com/in/ram-goenka/}{\underline{linkedin.com/in/ram-goenka/}} $|$
    \href{https://github.com/RamGoenka}{\underline{github.com/RamGoenka}} $|$
    \href{http://ramgoenka.com/}{\underline{ramgoenka.com}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois Urbana-Champaign}{Aug. 2021 - May 2024}
      {Bachelor of Science, Mathematics, Minor in Computer Science \& Statistics}{GPA: 3.71}
      \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Relevant Coursework}{: Abstract Linear Algebra, Data Structures, Differential Equations, Fundamental Mathematics, Introduction to Computer Science II, Number Theory, Statistics \& Probability I} \\
    }}
 \end{itemize}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Software Development Intern}{Sep. 2022 - Present}
  {National Center for Supercomputing Applications}{~~}
  \resumeItemListStart 
  \resumeItem{Used React.js to develop a web interface for the National Center for Atmospheric Research (NCAR), with supervision from Professor Nicole Riemer and Matthew Dawson.}
  \resumeItem{Developed graphical time-series models to track aerosol particle concentrations and other atmospheric chemical simulations using JavaScript and parsing CSV files.}
  \resumeItem{Added support for large input files on the website and improved communication and efficiency between frontend and backend to allow for more data points to be inputted to increase accuracy of outputted graphical models.}
    \resumeItemListEnd
  \resumeSubheading
  {STAT 107: Data Science Discovery - Course Assistant}{Aug. 2022 - Present}
  {University of Illinois Urbana-Champaign}{~~}
  \resumeItemListStart
    \resumeItem{Facilitated and led weekly Python lab sections. Helped students understand lab prompts and solve programming problems. Troubleshot technical issues relating to Git, Visual Studio Code, and Python.}
    \resumeItem{Held weekly office hours for over 550+ students to help them understand data science, programming, and statistics concepts, solve homework problems, and lab assignments, and provide exam reviews.}
    \resumeItemListEnd
    \resumeSubheading
      {University of Illinois Department of Computer Science - Course Staff}{May 2022 - Present}
      {CS 124: Introduction to Computer Science I -- Course Assistant}{~~}\\
      \resumeItemListStart
        \resumeItem{Supported 100+ students learn the fundamentals of the Java programming language through online office hours.}
        \resumeItemListEnd
        \vspace{-3pt}
        \emph{CS 124: Introduction to Computer Science I - Course Associate}%{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Aug. 2022 - Present}
        \vspace{-6pt}
        \resumeItemListStart
        \resumeItem{Assisted and guided 900+ students with learning the basics of computer science and the Java programming language by holding online office hours, monitoring the course forum, and recording homework walkthroughs.}
        \resumeItem{Supported student learning by helping solve homework problems, Machine Projects (MPs), debugging code, and understanding concepts. Mentored 4 Course Assistants to familiarize them with the course interface.}
        \resumeItemListEnd
    \resumeSubheading
      {NASA L'SPACE Mission Concept Academy - Team Lead Mathematician}{Jan. 2022 -- Apr. 2022}
      {The National Aeronautics and Space Administration}{~~~~~~}
      \resumeItemListStart
        \resumeItem{Researched computing methods to record and transmit seismic data in order to record the ground motion of the Moon and better detect Moonquakes.}
        \resumeItem{Conducted studies for battery systems to select the optimal power input unit within budget constraints.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{EAT-INI (Website)} $|$ \emph{Python, Flask, React, HTML, CSS, JavaScript, Git} \href{https://github.com/CS196Illinois/Group1-SP22}{\color{blue}[GitHub Repository]}}{~~~}
          \resumeItemListStart
            \resumeItem{Collaborated in a team of 4 students to develop a website for on-campus students, faculty, and visitors to find eatery options based on user input.} 
            \resumeItem{Worked on the frontend and built the user input system of the website using CSS, HTML and JavaScript. Worked on connecting the frontend to the backend, which used a Google Maps API key.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pixel (Discord Bot)} $|$ \emph{Python, Git} \href{https://github.com/RamGoenka/pixel}{\color{blue}[GitHub Repository]}}{~~~}
          \resumeItemListStart
            \resumeItem{Developed a Discord chat bot with a variety of features, and deployed it on a web-server for 24/7 functionality.}
            \resumeItem{Features include greetings, image sending, calculator functionality, and interactive games.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{MultiMode (Google Chrome Extension)} $|$ \emph{HTML, CSS, JavaScript, manifest.JSON, Git} \href{https://github.com/RamGoenka/MutliMode}{\color{blue}[GitHub Repository]}}{~~~}
          \resumeItemListStart
            \resumeItem{Built a Google Chrome extension that allows users to switch from light mode to dark mode. User can also set custom background options based on preference.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    
%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.10in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, \CC, JavaScript, HTML, CSS, R, Kotlin, TypeScript, Mathematica, \LaTeX} \\
     \textbf{Tools}{: React.js, Node.js, Gatsby.js, Flask, Git, Pandas, Matplotlib, Docker, NumPy, SciPy, Django, Bash, Catch2, GDB} 
    }}
 \end{itemize}
%-------------------------------------------
\end{document}

